Computer Science House Constitution

### 2025-10-27 constitution.tex
Remove Social Event Requirements
Removed CSH Social Event requirement from both Intro Member and Voting Member expectations.
Semesterly Gatekeep

The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic year.
Any of these requirements may be waived by the Evals Director or an E-Board Vote.
\begin{enumerate}
	\item Attend all House Meetings
	\item Attend at least six directorship meetings
	\item Attend at least one CSH social event
	\item Attend at least two Technical Seminars
\end{enumerate}

>>>>

The following requirements must be met for an Active Member to be allowed to vote after the first Intro Evals of the academic semester.
Any of these requirements may be waived by the Evals Director or an E-Board Vote.
\begin{enumerate}
	\item Attend at least six House Meetings
	\item Attend at least six directorship meetings
	\item Attend at least one CSH social event
	\item Attend at least two Technical Seminars
\end{enumerate}
